\documentclass[Dissertation.tex]{subfiles}
\begin{document}
\chapter*{Abstract}


\chapter{Introduction}
%% ADD IN SOME SOURCES

In the contemporary era, the rate at which user generated content is created and uploaded online has grown at an exponential rate, and for many people life without the internet and social media is now unimaginable. A result of this growth is the unprecedented amount of opinionated content freely available on the internet, ranging from tweets about current events to restaurant reviews on TripAdvisor. Such content is of great value to many interested parties, be they political researchers surveying public support, marketing executives seeking product feedback or researchers pushing the boundaries of modern technology.

It therefore comes as no surprise that a great deal of research effort in recent years has focussed on gaining understanding and meaning from opinionated content, namely in the field of Natural Language Processing (NLP). Research interest has primarily focussed on the categorizing the polarity of sentiment expressed in text. However, there is growing interest in the problem of stance detection. This takes sentiment analysis one step further, aiming to classify the opinion expressed in text with respect to a target topic, proposition or idea. While stance detection is a relatively recent field within NLP, the notions of speaker stance and stancetaking are well researched areas of linguistics. While in NLP the stance of text is generally limited to the categories of \textit{in favour}, \textit{neutral} or \textit{against}, linguistic perspectives on stance go well beyond this simple framework. Linguistic categorisations of stance can therefore provide a much richer picture of the subjectivity and sentiment expressed in text. There has been limited adoption of such frameworks within stance detection, however recent work has led to the creation of a novel dataset annotated for stance from a linguistics perspective, the Brexit Blog Corpus \cite{simakiAnnotatingSpeakerStance2017}. This dataset is of great importance since it challenges the current status-quo of stance detection in two ways. Firstly

In this project we examine approaches to performing stance detection using this novel dataset. Additionally the use of a novel model agnostic
\begin{comment}

The political landscape of the western world in recent years has changed dramatically. With many nations suffering economic crises and witnessing an influx of refugees fleeing violence and war in the middle east, huge swathes of voters across the western hemisphere are rejecting the prevailing centrist dogma in favour of populist, nationalist, xenophobic right wing movements. In continental Europe nationalist parties now have a significant presence in the governments of Hungary, Poland, Austria, Italy and Germanys 

 %\cite{krisztinaHungaryStrongmanViktor2018}, %\cite{marcinPolandEuroscepticsWin2015}, %\cite{gavinItalyConteSworn2018},
%\cite{kirstiAustriaKurzStrikes2017}, %\cite{michelleGermanyJubilantFarright2017}. % Source required	
In America traditional republican candidates lost the primaries to the demagoguery of Donald Trump, while establishment candidate Hillary Clinton failed to energise the centre-left vote% \cite{ericTrumpWinsElectoral2016}. 

There are a great number of socio-political and economic factors that can explain the expansion of the far right in Europe and America, but modern technology has almost certainly catalysed its rise to prominence. In particular, this is characterised by two related but opposing phenomena: the democratisation of journalism and the proliferation of hyper-polarized echo-chambers. The hegemony of corporate giants and state broadcasters has been disrupted by the explosion of social media and micro-blogging:  world events are now documented in real time on Twitter and Facebook live streams, and any person with a computer can now publish a blog for the world to read. It is easier than ever to access and consume news from countless different sources, yet Gaughan \cite{gaughanIlliberalDemocracyToxic2017} argues that a toxic mix of fake news, hyperpolarization and electoral manipulation has led to partisan divides being greater than ever. Political opinions are polarized and hardened by ranking algorithms that prioritise sensationalism and emotion over veracity and integrity, while internet hyper connectivity provides radical, fringe viewpoints a platform around which to build communities safe from critical debate. 

Following a a long and bitterly fought political campaign spearheaded by the United Kingdom Independence Party (UKIP), in 2016 the world looked on in shock as Britain voted to leave the EU by national referendum. Drawing many parallels to the election victory of Donald Trump, the Brexit referendum was marked by misinformation, vehement partisanship and an outcome that polls failed to predict.

In such politically turbulent times there is significant interest in applying machine learning and natural language processing (NLP) techniques to political social media content, such as opinion mining and sentiment analysis. This project considers the related task of stance detection, which in the simplest case involves determining if a text in agreement or disagreement with a given proposition. As one of the most significant and polarizing political events in a generation, the Brexit debate is an ideal topic for investigating stance detection.
\end{comment}

\section{Aims and Objectives}
This project aimed to investigate stance detection using the Brexit Blog Corpus, a publicly available dataset created by Simaki et al \cite{simakiAnnotatingSpeakerStance2017}. The data set is comprised of texts extracted from public blog posts written in 2016 concerning the upcoming British referendum on European Union membership. Neural approaches were investigated and compared to kernel based methods, and the relationship between multi-class, multi-label and multi-task learning problems was explored. Key design considerations were simplicity, efficiency and interpretability - all methods can feasibly be run on home computers without needing any GPU acceleration. Each method was benchmarked using standard metrics and its performance was improved using hyper-parameter tuning techniques.

\section{Report Structure}
Following this opening chapter, the report begins with Chapter 2, a literature survey that serves as background reading for the topics investigated in the report. The survey including definitions of stance, previous work in stance detection, and a short review of relevant machine learning technologies. Following the review, in Chapter 3 the Brexit Blog Corpus dataset is examined in a process of exploratory data analysis that includes visualization and summarization of the dataset. In Chapter 4, the project methodology is outlined and additionally the design and implementation of classifiers is described. Finally, the project results are displayed and analysed in Chapter 5, and we conclude with a project summary and future work in Chapter 6.
%tell them what you are going to tell them
\end{document}